Spec2Fab: A Graph-Based Framework for Fabricating Fabrication Algorithms

### 2012-12-21 paper.tex
Editing results

Computing material assignments at output device resolution is computationally inefficient. Because of this, material assignments are computed  using a reduced representation. We specify this representation using a Reducer Network.  This structure is conceptually similar to those used in programmable shading systems (e.g. ~\cite{Cook1984}, Maya Shader Networks) . However these systems are primarily concerned with assigning known materials and textures to an object's surface whereas we are seeking a volumetric assignment of (as yet) unknown materials. In order to accomplish this task we build a directed, acyclic graph which has the object's surface geometry as its root node. We define two classes of nodes, geometry nodes and parameterization nodes. A geometry node takes a volumetric region as input and produces a partition of unity of this region as output. The leaf nodes of our graph are the parameterization nodes which associate a material assignment function of the form $\lambda\left(x,y,z,\theta\right)$ to an input volumetric region. Lambda can either output material parameters or a discrete material assignment for a spatial point $\left(x,y,z\right)$ given some parameters, here denoted by $\theta$. Because the network describes a nested set of partitions of unity we can efficiently perform material queries by passing a query point through the network until it arrives at a parameterization node. We note that Reducer Networks do not inherently enforce material continuity between disjoint regions in the graph, however, for material assignment problems this is neither required nor desired.

@@

\note{I think we should just go with the results we have, texture etc... show the reducer network, tuner network, simulated results and manufactured result (if you have them}
\section{Results and Discussion}
Table~\ref{tab:built-in} shows a list of nodes implemented in our framework. With this set of nodes we can reproduce all previous work previously discussed. This validates our assertion, that the space of fabrication  algorithms can be spanned effectively using the Reducer and Tuner networks. Secondly it illustrates how we can leverage component reuse to quickly create such algorithms. Table~\ref{tab:example} lists the components of the framework used to recreate each example.
\begin{table*}
\centering
\begin{tabular}{lc}
\hline 
\textbf{Reducer Node} & \textbf{Description} \\
Geometry Nodes &\\
\hline
InputMesh & Loads shape to which materials will be assigned\\\
Stratum & Divides an input volume into an outer layer of given thickness and an interior blob\\
Column & Divides an input volume into a number of columns\\
\hline
Material Nodes &\\
\hline
ConstantMaterial & Assigns a constant material to an input volume \\
LayeredMaterial &  Assigns a layered set of materials to an input volume \\
QuadLayerMaterial & ??? \\
SubdivSurfMateral & ??? \\
\hline
\end{tabular}
\caption{Components we implemented and used in the experiments.}
\label{tab:built-in}
\end{table*}

@@

\subsection{Refractive Caustics}
We have also implemented two algorithms for computing goal-based caustics;  ~\cite{Marios:2011} and ~\cite{Finckh:2010}.
The first version of this algorithm computes  a set of micro-lenses which produce the desired caustic image. The optimization applies simulated annealing in order to permute the location of these micro-lenses in order to achieve a smooth surface. Of note is the fact that this algorithm does not quire a simulation algorithm. Despite this it is still implementable within our framework.

In the second algorithm , we use subdivision surfaces to represent a smooth caustic caustic surface. This is in contrast to the potentially discontinuous surface in the method above. The original algorithm used B-spline surfaces. We also replace the specialized renderer from the original publication with a generic, fast caustics rendering technique ~\cite{Yuksel:2009}. Our algorithm took 6 hours to finish with $4000$ control points for the model and $600\times 600$ resolution for the caustic image.  A picture of our printed result under desired lighting is shown in Figure~\ref{fig:caustic}.
\begin{figure}
	\centering
 	\includegraphics[width=0.3\textwidth]{figure/caustic.jpg}
\caption{Teapot with a caustic image.}
\label{fig:caustic}
\end{figure}

\subsection{Subsurface Scattering and Deformation}
We first replicated \cite{Bickel:2010} to print materials with specified elasticity. We then combined it with subsurface scattering
matching to print material that approximates both the subsurface scattering property and the deformation behavior. The result is shown in Figure~\ref{fig:deform}. In our case we perform coupling at the tuner level by alternating tuner execution for the two
separate problems. This shows how our framework can facilitates the creation of new fabrication problems by allowing easy reuse of previous work and also providing a ``playground'' in which one can explore different computational approaches.
%We tried different combinations of generators in this experiment.
%We compared the performance of these different generator
%in terms of run-time and error.
%\begin{enumerate}
%\item Spline for top layer, fine-grained voxelization for mid layer
%and a coarse grid for bottom layer.
%\item Voxels for top layer, splines for middle layer and a coarse
%bottom layer.
%\item Find-grained voxels for top layer and coarse grid for bottom layer.
%\end{enumerate}

@@

Two error plots showing subsurface scattering and deformation errors decrease
after each iteration in Figure~\ref{fig:err}.

@@

\subsection{New Examples for Mechanical Properties}
%Ball bounce to certain height. We used a higher resolution
%grid for the out layer and very low resolution
%for the inner mesh.
%
%A plot of bounce height after each iteration.
%The height and desired height is plotted in Figure~\ref{fig:ball}
%\begin{figure}
%	\centering
% 	\includegraphics[width=0.3\textwidth]{figure/ballHeight.pdf}
%\caption{Simulated height per-iteration of a ball bouncing after free-falling at 1 meter height.
%	Redline is desired height.}
%\label{fig:ball}
%\end{figure}

A loaded die as shown in Figure~\ref{fig:die}. 
This example is a showcase for a global optimization algorithm
because a local change of material assignment will influence the global behavior.
We used very high resolution grid for the surface to match texture
of a die. The inner lay has only $3\times 3$ resolution.
\begin{figure}
	\centering
 	\includegraphics[width=0.25\textwidth]{figure/die.png}
\caption{A printed loaded die}
\label{fig:die}
\end{figure}
It has a certain probability to land on "1".
A table of probability distribution of landing on each side
is shown in Table~\ref{tab:dice}.

\begin{table}
\centering
  \begin{tabular}{ |c| p{0.7in} | p{0.7in} | }
  \hline
  face & simulated probability & measured probability\\
  \hline
  1 & 0.5 & 0.5\\
  \hline
  2 & 0.1 & 0.1\\
  \hline
  3 & 0.1 & 0.1\\
  \hline
  4 & 0.1 & 0.1\\
  \hline
  5 & 0.1 & 0.1\\
  \hline
  6 & 0.1 & 0.1\\

  \hline
  \end{tabular}
  \caption{Simulated and measured dice probability}
  \label{tab:dice}
\end{table}

A plot of simulated probability of landing on "1" after each iteration
is shown in Figure~\ref{fig:dieErr}.

\begin{figure}
	\centering
 	\includegraphics[width=0.3\textwidth]{figure/die.pdf}
\caption{Probability of die landing on 1 after each iteration.}
\label{fig:dieErr}
\end{figure}

Printer:objet, ours.

More ideas:
balancing bird with texture.
%%\section{Possible Extension}
%%UI to specify input deformation.
\section{Limitations and Future Work}

>>>>

Computing material assignments at output device resolution is computationally inefficient. Because of this, material assignments are computed  using a reduced representation. We specify this representation using a Reducer Network.  This structure is conceptually similar to those used in programmable shading systems (e.g. ~\cite{Cook1984}, Maya Shader Networks) . However these systems are primarily concerned with assigning known materials and textures to an object's surface whereas we are seeking a volumetric assignment of (as yet) unknown materials. In order to accomplish this task we build a directed, acyclic graph which has the object's surface geometry as its root node. We define two classes of nodes, geometry nodes and parameterization nodes. A geometry node takes a volumetric region as input and produces a partition of unity of this region as output. The leaf nodes of our graph are the parameterization nodes which associate a material assignment function of the form $\lambda\left(x,y,z,\theta\right)$ to an input volumetric region. Lambda can either output material parameters or a discrete material assignment for a spatial point $\left(x,y,z\right)$ given some parameters, here denoted by $\theta$. We allow our material assignment nodes to assign a void material to regions of the mesh. This allows us to treat surface displacements and material assignments in a unified fashion. Because the network describes a nested set of partitions of unity we can efficiently perform material queries by passing a query point through the network until it arrives at a parameterization node. We note that Reducer Networks do not inherently enforce material continuity between disjoint regions in the graph, however, for material assignment problems this is neither required nor desired.

@@

\note{I think we should just go with the results we have, texture etc... show the reducer network, tuner network, simulated results and manufactured result (if you have them}
\section{Results and Discussion}
Table~\ref{tab:built-in} shows a list of nodes implemented in our framework. With this set of nodes we can reproduce all work previously discussed. This validates our assertion, that the space of fabrication  algorithms can be spanned effectively using the Reducer and Tuner networks. Secondly it illustrates how we can leverage component reuse to quickly create such algorithms.\autoref{tab:example} lists the components of the framework used to recreate each example.
\begin{table*}
\centering
\begin{tabular}{lc}
\hline 
\textbf{Reducer Node} & \textbf{Description} \\
Geometry Nodes &\\
\hline
InputMesh & Loads shape to which materials will be assigned\\\
Stratum & Divides an input volume into an outer layer of given thickness and an interior blob\\
Column & Divides an input volume into a number of columns\\
\hline
Material Nodes &\\
\hline
ConstantMaterial & Assigns a constant material to an input volume \\
LayeredMaterial &  Assigns a layered set of materials to an input volume \\
QuadLayerMaterial & ??? \\
SubdivSurfMateral & ??? \\
\hline
\end{tabular}
\caption{Components we implemented and used in the experiments.}
\label{tab:built-in}
\end{table*}

@@

\subsection{Refractive Caustics}
We have also implemented two algorithms for computing goal-based caustics;  ~\cite{Marios:2011} and ~\cite{Finckh:2010}.
The first version of this algorithm computes  a set of micro-lenses which produce the desired caustic image. The optimization applies simulated annealing to permute the location of these micro-lenses in order to construct a smooth surface. Of note is the fact that this algorithm does not quire a simulation algorithm. Despite this it is still implementable within our framework.

In the second algorithm, we use subdivision surfaces to represent a smooth caustic surface. This is in contrast to the potentially discontinuous surface in the method above. The original algorithm used B-spline surfaces however we have replaced these with a subdivision surface. We also replace the specialized renderer from the original publication with a generic, fast caustics rendering technique ~\cite{Yuksel:2009}. Our algorithm took 6 hours to finish with $4000$ control points for the model and $600\times 600$ resolution for the caustic image.  A picture of our printed result under desired lighting is shown in \autoref{fig:caustic}.
\begin{figure}
	\centering
 	\includegraphics[width=0.3\textwidth]{figure/caustic.jpg}
\caption{Teapot with a caustic image.}
\label{fig:caustic}
\end{figure}

\subsection{Subsurface Scattering and Deformation}
We first replicated \cite{Bickel:2010} to print materials with specified elasticity. We then combined it with subsurface scattering
matching to print material that approximates both the subsurface scattering property and the deformation behavior. The result is shown in Figure~\ref{fig:deform}. In our case we perform coupling at the tuner level by alternating tuner execution for the two
separate problems. Here we see that our framework facilitates the creation of new fabrication problems by allowing easy reuse of previous work and also providing a ``playground'' in which one can explore different computational approaches. \autoref{fig:err} contains two error plots showing that the subsurface scattering and deformation errors decrease after each tuner iteration.

%We tried different combinations of generators in this experiment.
%We compared the performance of these different generator
%in terms of run-time and error.
%\begin{enumerate}
%\item Spline for top layer, fine-grained voxelization for mid layer
%and a coarse grid for bottom layer.
%\item Voxels for top layer, splines for middle layer and a coarse
%bottom layer.
%\item Find-grained voxels for top layer and coarse grid for bottom layer.
%\end{enumerate}

@@

@@

%\subsection{New Examples for Mechanical Properties}
%%Ball bounce to certain height. We used a higher resolution
%%grid for the out layer and very low resolution
%%for the inner mesh.
%%
%%A plot of bounce height after each iteration.
%%The height and desired height is plotted in Figure~\ref{fig:ball}
%%\begin{figure}
%%	\centering
%% 	\includegraphics[width=0.3\textwidth]{figure/ballHeight.pdf}
%%\caption{Simulated height per-iteration of a ball bouncing after free-falling at 1 meter height.
%%	Redline is desired height.}
%%\label{fig:ball}
%%\end{figure}
%
%
%A loaded die as shown in Figure~\ref{fig:die}. 
%This example is a showcase for a global optimization algorithm
%because a local change of material assignment will influence the global behavior.
%We used very high resolution grid for the surface to match texture
%of a die. The inner lay has only $3\times 3$ resolution.
%\begin{figure}
%	\centering
% 	\includegraphics[width=0.25\textwidth]{figure/die.png}
%\caption{A printed loaded die}
%\label{fig:die}
%\end{figure}
%It has a certain probability to land on "1".
%A table of probability distribution of landing on each side
%is shown in Table~\ref{tab:dice}.
%
%\begin{table}
%\centering
%  \begin{tabular}{ |c| p{0.7in} | p{0.7in} | }
%  \hline
%  face & simulated probability & measured probability\\
%  \hline
%  1 & 0.5 & 0.5\\
%  \hline
%  2 & 0.1 & 0.1\\
%  \hline
%  3 & 0.1 & 0.1\\
%  \hline
%  4 & 0.1 & 0.1\\
%  \hline
%  5 & 0.1 & 0.1\\
%  \hline
%  6 & 0.1 & 0.1\\
%
%  \hline
%  \end{tabular}
%  \caption{Simulated and measured dice probability}
%  \label{tab:dice}
%\end{table}
%
%A plot of simulated probability of landing on "1" after each iteration
%is shown in Figure~\ref{fig:dieErr}.
%
%\begin{figure}
%	\centering
% 	\includegraphics[width=0.3\textwidth]{figure/die.pdf}
%\caption{Probability of die landing on 1 after each iteration.}
%\label{fig:dieErr}
%\end{figure}
%
%Printer:objet, ours.
%
%More ideas:
%balancing bird with texture.
%%%\section{Possible Extension}
%%%UI to specify input deformation.
\section{Limitations and Future Work}
